\textbf{Contributed by Pablo Arantes}

Molecular dynamics (MD) simulations are widely used for describing biomolecular motion, employing a classic physics approximation to depict atomic trajectories \cite{Liu2017,Hollingsworth2018}. However, due to their high computational demands, there is an increasing effort to enable large-scale runs of MD simulations \cite{Hollingsworth2018}. Cloud computing has emerged as a potential solution due to its scalability, reliability, and cost-effectiveness \cite{Ebejer2013}. Nevertheless, utilizing cloud computing for MD simulations requires technical expertise and the ability to perform tedious tasks, such as configuring remote nodes and installing software. To address this challenge, we developed a user-friendly front-end for running MD simulations \cite{Arantes2021} using the OpenMM toolkit \cite{Eastman2017} on the Google Colab framework \cite{colab,Bisong2019} (\url{https://pablo-arantes.github.io/making-it-rain/}). Our approach involves shareable, ready-to-use, and customizable Jupyter notebooks that guide the end-user through the process of running their calculations on the Google Colab platform. This approach makes it more accessible for low-income research groups to perform MD simulations at the microsecond timescale, and also facilitates teaching and learning of molecular simulations. These protocols can be customized for specific use cases, providing students with a hands-on approach to learning MD simulations.

We believe that our work has a significant impact in the scientific community by enabling more researchers to conduct MD simulations without the high cost of traditional computing resources. This approach is also valuable for educators who wish to provide students with a hands-on experience in MD simulations. In summary, our approach offers an affordable and accessible solution for performing MD simulations using cloud computing resources. We hope that this strategy will empower researchers and educators alike, ultimately leading to new insights and discoveries in the field of biomolecular dynamics.

All notebooks presented here are freely and publicly available at  \url{https://pablo-arantes.github.io/making-it-rain/}.